 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-06-14 analysis/paper/shceof.Rmd
Mueve sección de si existe el SAM

\textcolor{red}{Creo que te había hecho el mismo comentario en la versión anterior. Tenés que ser más preciso cuando hablas/mostras regresiones indicando en qué dirección va la regresión "regressed upon". Revisalo a lo largo del texto. En la figura 5, ¿no está al revés?}

\textcolor{red}{En el caption de la Figura 5 falta aclarar qué son los puntos.}

@@

Figure  \@ref(fig:t-vertical) shows the vertical distribution of the regression coefficientes on cEOF1 from zonal anomalies of air temperature and zonal anomalies of ozone mixing ratio averaged between `r knitr::combine_words(LatLabel(o3wave_lats))`.
\textcolor{red}{Deberias aclarar qué significa la terminología que estas utilizando. Lo podes hacer en los métodos y ya queda para todo el texto}.
Temperature zonal anomalies associated with cEOF1 show a clear wave 1 pattern for both real and imaginary components throughout the atmosphere above 250 hPa with a change in sign above 10 hPa.
Following hydrostatic balance, this is the level in which the geopotential anomaly have maximum amplitude (not shown).

@@

\textcolor{red}{Revisa que todos los captions tengan las unidades correspondientes}

@@

<!-- As a further illustration \textcolor{red}{(¿De qué?)}, Figure\ @ref(fig:eof-filtered) shows the spatial pattern of the leading EOF of 200 hPa geopotential height when the variability associated with cEOF2 is removed. The resulting pattern is an nearly zonally symmetrical annular mode. This mode is highly correlated with SAM (`r eof_filtered_cor[term == "full"]$text`), but only with the symmetrical part (`r eof_filtered_cor[term == "sym"]$text`). Note that the usual definition of the PSA modes as the second and third EOFs creates modes orthogonal to the SAM (defined as the first EOF) and thus impedes this kind of filtering.   -->

@@

```{r fake_eof}
cEOF2 <- ceof$eof[[1]]$left[cEOF == "cEOF2"] %>% 
  copy() %>% 
  .[, cEOF := NULL] %>% 
  .[]

@@

\textcolor{red}{Esta parte creo que quedaría mejor como una subsección, aunque no se me viene rápido a la cabeza el título y la pondría después de la parte de PSA}

@@

This suggests that the zonal asymmetries of the SON SAM could very well be mostly a statistical artefact.
Since many surface impacts are mediated by the asymmetric component, as well as the relationship between SAM and ENSO [@campitelli2021], this potential issue could affect the interpretability of many results involving the SAM.
Studies on the relationship between the SAM and PSA-like patterns would be particularly difficult to interpret.

## Tropical sources

@@

(ref:sst-psi-2-cap) Regression maps of cEOF2 with SST (column a) and streamfunction zonal anomalies (shaded) with their corresponding activity wave flux (vectors) (column b). Areas marked with dots have p-values smaller than 0.05 adjusted for FDR.

>>>>

@@

Figure \@ref(fig:t-vertical) shows the vertical distribution of the regression coefficients on cEOF1 from zonal anomalies of air temperature and zonal anomalies of ozone mixing ratio averaged between `r knitr::combine_words(LatLabel(o3wave_lats))`.
\textcolor{red}{Deberias aclarar qué significa la terminología que estas utilizando. Lo podes hacer en los métodos y ya queda para todo el texto}.
Temperature zonal anomalies associated with cEOF1 show a clear wave 1 pattern for both real and imaginary components throughout the atmosphere above 250 hPa with a change in sign above 10 hPa.
Following hydrostatic balance, this is the level in which the geopotential anomaly have maximum amplitude (not shown).

@@

@@

### Is the Asymmetric SAM real?

@@

```{r make_fake_eof}
cEOF2 <- ceof$eof[[1]]$left[cEOF == "cEOF2"] %>% 
  copy() %>% 
  .[, cEOF := NULL] %>% 
  .[]

@@

@@

This suggests that the zonal asymmetries of the SON SAM could very well be mostly a statistical artefact.
Since many surface impacts are mediated by the asymmetric component, as well as the relationship between SAM and ENSO [@campitelli2021], this potential issue could affect the interpretability of many results involving the SAM.
Studies on the relationship between the SAM and PSA-like patterns would be particularly difficult to interpret.
## Tropical sources

@@

(ref:sst-psi-2-cap) Regression maps of cEOF2 with SST (column a) and streamfunction zonal anomalies (shaded) with their corresponding activity wave flux (vectors) (column b). Areas marked with dots have p-values smaller than 0.01 adjusted for FDR.
